On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-07-30 manuscripts/IEEE/final_submission.tex
fixed minor bug
Updates from Overleaf

It is our hope that the theoretical tools showcased here will be of some use to the community in answering these remaining questions.

@@

\textbf{Acknowledgement.} We thank Fritz Sommer for turning our attention to the dictionary learning problem and Darren Rhea for sharing early explorations. We also thank Ian Morris for posting a reference to his proof of \eqref{eqdim} online at Stack Exchange. Finally, we thank Bizzyskillet (www.soundcloud.com/bizzyskillet) for the “No-Exam Jams”, to which many of our proofs were designed and constructed.}

>>>>

It is our hope that the theoretical tools showcased here will be of use to the community in answering these remaining questions.

@@

\textbf{Acknowledgement.} We thank Fritz Sommer for turning our attention to the dictionary learning problem and Darren Rhea for sharing early explorations. We also thank Ian Morris for posting a reference to his proof of \eqref{eqdim} online at Stack Exchange. Finally, we thank Bizzyskillet (www.soundcloud.com/bizzyskillet) for ``The No-Exam Jams'' to which many of our proofs were designed and constructed.
